\begin{document}
%============================================================================%
%	DOCUMENT CONTENT
%============================================================================%
\fcolorbox{bgreycol}{maya}{
\begin{minipage}[c][0.96\textheight][t]{0.7\linewidth}

%---------------------------------------------------------------------------------------
%	HEADER SECTION
%----------------------------------------------------------------------------------------

<HEADER>

%============================================================================%
%
%	MAIN CONTENT
%
%============================================================================%

%---------------------------------------------------------------------------------------
%	STATUS
%----------------------------------------------------------------------------------------
\cvsection{About}

\colorbox{fgreycol}{
	\parbox{0.969\linewidth}{
		\parbox{0.45\linewidth}{
			\begin{itemize}
				\item[\larrow{softcol}] \textcolor{lightcol}{\textbf{Age: <AGE> years}}
				\item[\larrow{softcol}] \textcolor{lightcol}{\textbf{Birthday: 14 Sept 1992}}
				\item[\larrow{softcol}] \textcolor{lightcol}{\textbf{Hometown: Guaymas, Son}}
				\item[\larrow{softcol}] \textcolor{lightcol}{\textbf{Residency: Hermosillo, Son}}
			\end{itemize}
		}
		\parbox{0.45\linewidth}{
			\begin{itemize}
    			\item[\larrow{softcol}] \textcolor{lightcol}{\textbf{Civil Status: Single}}
				\item[\larrow{softcol}]	\textcolor{lightcol}{\textbf{English: Speak 80\%, Write 90\% }}
			\end{itemize}
		}
	}
}

%---------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\cvsection{Experience}

\event{May-Ago 2015}{Professional Practices}{CFE, Hermosillo}{Training in the water treatment plant, participating as assistant to the chemical engineer in charge of the area.}

\cvevent{Jun-Sep 2018}{Scientific Investigation}{UNAM, Oaxaca}{Studies about numerical methods to solve stochastic partial differential equations.}{The article publication can be consulted at the following button. \hspace{6mm} \href{https://www.researchgate.net/publication/334330862_INITIAL_CONDITIONS_CONTINUITY_OF_A_NUMERICAL_APPROXIMATION_FOR_KOLMOGOROV_EQUATIONS/}{\colorbox{darkcol}{\colorbox{lightcol}{\hspace{3mm}\textcolor{fgreycol}{\textbf{get-info}} \hspace{1.5mm} \icon{Info}{8}{fgreycol}\hspace{0.5mm}}}}}

\cvevent{2017 - 2019}{Programming workshops}{Unison, Hermosillo}{Workshops on introducing the language and its use to solve engineering problems.}{The class material can be consulted at the following button. \hspace{10mm} \href{https://github.com/CircuitalMinds/jupyter/tree/main/nbs/}{\colorbox{darkcol}{\colorbox{lightcol}{\hspace{3mm}\textcolor{fgreycol}{\textbf{git-page}} \hspace{1.5mm} \icon{Github}{8}{fgreycol} \hspace{0.5mm}}}}}

\event{2020 - 2021}{Developer Full-Stack}{Necodex}{Frontend and Backend Developer, DevOps, Quality Assurance, QA Automation.}

\event{2021 - 2023}{Plant Operations Engineer}{Windstar LPG}{Control and management of inventories, preparation and approval of mass balances in refined petroleum products, Purchase and sale of LPG, personnel management, Supply chain activities for road transport and retail trade. \\[6pt]}

%---------------------------------------------------------------------------------------
%	EDUCATION SECTION
%--------------------------------------------------------------------------------------
\cvsection{Education}

\cvevent{2017 - 2019}{
	Master's Degree in Mathematical Sciences}{Unison, Hermosillo}{Thesis: Numerical Solutions to the Stochastic and Deterministic Burgers Equation Using Spectral Methods.
}
{
	Click on the following button to download the thesis file: \hspace{10.5mm} \href{https://raw.githubusercontent.com/alanmatzumiya/alanmatzumiya.github.io/main/assets/portfolio/master/thesis.pdf}{\colorbox{darkcol}{\colorbox{lightcol}{\textcolor{fgreycol}{\hspace{3mm}\textbf{PDF}} \hspace{1.5mm} \icon{Download}{8}{fgreycol}\hspace{3mm}}}}
}

%\textcolor{sectcol}{\hrule}
%
\cvevent{2011 - 2016}{Bachelor's Degree in Chemical Engineering}{Unison, Hermosillo}{
	Thesis: Caracterizaci\'on y evaluaci\'on de las propiedades bioactivas de una mezcla de biocomp\'ositos de hidroxiapatita / $\beta$-wollastonita.
}
{
	Click on the following button to download the thesis file: \hspace{10.5mm} \href{https://raw.githubusercontent.com/alanmatzumiya/alanmatzumiya.github.io/main/assets/portfolio/bachelor/thesis.pdf}{\colorbox{darkcol}{\colorbox{lightcol}{\textcolor{fgreycol}{\hspace{3mm}\textbf{PDF}} \hspace{1.5mm} \icon{Download}{8}{fgreycol}\hspace{3mm}}}}
}

%---------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%--------------------------------------------------------------------------------------

<SIDEBAR>

%-------------------------------------------------------------------------------------------------
%	ARTIFICIAL FOOTER (fancy footer cannot exceed linewidth)
%--------------------------------------------------------------------------------------------------

\null
\vspace*{\fill}
\hspace{-0.25\linewidth}\colorbox{darkcol}{
	\makebox[1.45\linewidth][c]{
		\mystrut \small \textcolor{lightcol}{
			Coypright <CURRENT-YEAR> Alan Matzumiya}
	}
}

\vspace{1mm}
}

%---------------------------------------------------------------------------------------
%	NEW PAGES
%--------------------------------------------------------------------------------------

<PAGE-CONTENT>

\end{document}
%============================================================================%
%
%	DOCUMENT END
%============================================================================%
